%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Deedy - One Page Two Column Resume
% LaTeX Template
% Version 1.2 (16/9/2014)
%
% Original author:
% Debarghya Das (http://debarghyadas.com)
%
% Original repository:
% https://github.com/deedydas/Deedy-Resume
%
% IMPORTANT: THIS TEMPLATE NEEDS TO BE COMPILED WITH XeLaTeX
%
% This template uses several fonts not included with Windows/Linux by
% default. If you get compilation errors saying a font is missing, find the line
% on which the font is used and either change it to a font included with your
% operating system or comment the line out to use the default font.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% TODO:
% 1. Integrate biber/bibtex for article citation under publications.
% 2. Figure out a smoother way for the document to flow onto the next page.
% 3. Add styling information for a "Projects/Hacks" section.
% 4. Add location/address information
% 5. Merge OpenFont and MacFonts as a single sty with options.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% CHANGELOG:
% v1.1:
% 1. Fixed several compilation bugs with \renewcommand
% 2. Got Open-source fonts (Windows/Linux support)
% 3. Added Last Updated
% 4. Move Title styling into .sty
% 5. Commented .sty file.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
% Known Issues:
% 1. Overflows onto second page if any column's contents are more than the
% vertical limit
% 2. Hacky space on the first bullet point on the second column.
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%


\documentclass[]{deedy-resume}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\rfoot{Page \thepage \hspace{1pt}}
\begin{document}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     LAST UPDATED DATE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\lastupdated

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     TITLE NAME
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\namesection{Andrew}{Lawson}{ \urlstyle{same}\href{http://www.andrewlawson.us}{www.andrewlawson.us} | 
\href{mailto:aeriklawson@gmail.com}{aeriklawson@gmail.com} | 203.217.1768
}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN ONE
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{minipage}[t]{0.38\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EDUCATION
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Education}

\subsection{University of Connecticut}
\descript{BSE in Computer Science \& Engr.}
\descript{Minor in Mathematics}
\location{May 2015 | Storrs, CT}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     LINKS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Links}
GitHub: \href{https://www.github.com/aelawson}{\bf aelawson} \\
Facebook: \href{https://www.facebook.com/aeriklawson}{\bf aeriklawson} \\
LinkedIn:  \href{https://www.linkedin.com/in/aeriklawson}{\bf aeriklawson} \\
Twitter:  \href{https://www.twitter.com/aeriklawson}{\bf aeriklawson} \\

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     COURSEWORK
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Coursework}
\subsection{Graduate}
Machine Learning \\
\sectionsep

\subsection{Undergraduate}
Operating Systems \\
Programming Languages \\
Algorithms \& Complexity \\
Stochastic Processes

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     SKILLS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Skills}
\subsection{Proficient}
Python \textbullet{} Java \textbullet{} C\# \textbullet{} JavaScript \\
\sectionsep
\subsection{Prev. Experience}
C \textbullet{} C++ \textbullet{} PHP \textbullet{} Perl \textbullet{} \\
MySQL \textbullet{} PostgreSQL \textbullet{} \\
Git \textbullet{} SVN \textbullet{} Mercurial \textbullet{} CVS

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     ACTIVITIES
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Activities}
\location{2016}
Code for Boston \\
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Open Source Contributor
\end{tightemize}
Mozilla \\
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Open Source Contributor
\end{tightemize}
\location{2014 - 2015}
UConn Robotics Club \\
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Treasurer
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     AWARDS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Awards}
\location{2015}
University Scholar \\
%\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Highest academic distinction \\ awarded to undergraduates.
\end{tightemize}
Honors Scholar

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     INTERESTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Interests}
Long-distance running \textbullet{} Biking \textbullet{}
Ultimate frisbee \textbullet{} Restaurant crawls \textbullet{}
Video games \textbullet{} Movies \textbullet{} Guitar

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\end{minipage}
\hfill
\begin{minipage}[t]{0.61\textwidth}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     EXPERIENCE
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Experience}
\runsubsection{BBN Technologies}
\descript{| Software Engineer }
\location{Jun. 2015 - Present | Cambridge, MA}
\vspace{\topsep} % Hacky fix for awkward extra vertical space
\begin{tightemize}
\item Helped ship M3S, a distributed web application that provides automatic translation and analysis of foreign media sources.
\item Led development of a new core feature that aggregates users' translated social media posts.
\item Built with C\#, JavaScript, and ASP.NET MVC.
\end{tightemize}
\sectionsep

\runsubsection{Schwartz Lab}
\descript{| Software Developer }
\location{Aug. 2014 - May 2015 | Storrs, CT}
\begin{tightemize}
\item Shipped LincusAnalytics - a text analysis engine for identifying and comparing research funding across universities.
\item Wrote several automated scrapers used daily to mine web data, including HTML and GMail accounts.
\item All built with Python and MySQL. Deployed on Amazon EC2.
\end{tightemize}
\sectionsep

%\runsubsection{Royal Bank of Scotland}
%\descript{| Summer Tech Analyst }
%\location{Jun. 2014 - Aug. 2014 | Stamford, CT}
%\begin{tightemize}
%\item Created a Perl web app used by the entire derivatives desk to manage product portfolios.
%\item Worked on a tool that automates daily financial reports using Perl and T-SQL.
%\item Designed and taught a Raspberry Pi / Python class to an underprivileged middle school.
%\end{tightemize}
%\sectionsep

\runsubsection{UConn AITC}
\descript{| Software Engineering Intern}
\location{Jul. 2013 - Feb. 2014 | Storrs, CT}
\begin{tightemize}
\item Developed an interactive wall for Boston Children's Hospital's main lobby - used daily by visitors, staff, and patients.
\item Helped write a Kinect-based system that lets players use gestures to control on-screen avatars.
\item Designed and coded avatar behavior and a player tracking system.
\item Built with C\#, Unity3D, and Microsoft Kinect.
\end{tightemize}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%     PROJECTS
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\section{Projects}
\runsubsection{Netflix Comments} \\
\location{Apr. 2016 - Present}
\begin{tightemize}
\item Mobile app that adds a commenting system to Netflix. Made with React Native.
\item Created a Chrome extension that synchronizes Netflix timestamps using JavaScript and Socket.IO.
\item Developed a REST API / backend using Node.js, Redis, and PostgreSQL.
\end{tightemize}
\sectionsep

\runsubsection{ByPath (Code for Boston)} \\
\location{Jan. 2016 - Present}
\begin{tightemize}
\item Mobile routing app to make city-wide navigation easier for pedestrians with limited mobility.
\item Built with two teammates using AngularJS, Node.js, and PostgreSQL.
\item Published (in alpha) on the Apple App Store and Google Play.
\end{tightemize}
\sectionsep

\runsubsection{Autonomous Quadcopter} \\
\location{Jan. 2013 - May 2015}
\begin{tightemize}
\item Led R\&D of an autonomous quadcopter robot that generates a 3D map of GPS-denied environments using a Microsoft Kinect.
\item Worked with two senior capstone teams to create a navigation and sensor system using C++ and Arduino.
\item Developed a real-time, distributed system that fuses 3D point clouds generated by multiple robots using C++, PCL, and ROS.
\end{tightemize}
\sectionsep

\end{minipage}
\end{document}  \documentclass[]{article}
